A generalized quadratic estimate for random field nonstationarity \thanksref{code}

### 2016-02-28 paper/paper.tex
saving state before Joe takes a last look at draft 1

In what follows we derive a quadratic estimate of $\bs\theta(\bs x)$ for locally invariant nonstationarity of the form given in Definition \ref{Definition 1}. The estimates are derived under the observational scenario: a single realization of the nonstationary random field observed on a dense grid with additive stationary noise. These assumptions hold throughout the paper. We list them here to be completely explicit.

>>>>

In what follows we derive a quadratic estimate of $\bs\theta(\bs x)$ for locally invariant nonstationarity of the form given in Definition \ref{Definition 1}. The estimates are derived under the following observational scenario: a single realization of the nonstationary random field observed on a dense grid with additive stationary noise. These assumptions hold throughout the paper. We list them here to be completely explicit.
